Naturalness in U(1) extensions of the MSSM

### 2015-01-22 paper/e6ssm-tuning-paper.tex
removed comment that doens't need further addressing.
changed comment on BM2 to refelect new point..

[We should add some discussion about the $U(1)_I$ and the physics of
  that model here, since it has the lowest tuning.]

@@

By contrast the tuning for E$_6$SSM BM2 is very different.  This point
was chosen as it had much lighter stops and a gluino mass that is just
above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
not amongst the lowest tuned points, since at that scale the tree
level tuning from $M_{Z^\prime}$ dominates.  However the reduction in
$M_3$ means that $\Delta_{M_3}$ is substantially lower and only
becomes the dominant tuning very close to the GUT scale, giving a
tuning at $10^{16}$ GeV of $\approx 900$, which is below that of the
other two benchmark points.  Since large mixing was also used to
reduce allow lighter stops, we see initially a large contribution from
$\Delta_{A_t}$ as we did in the MSSM benchmark.  [Last thing that
  needs to be explained - why do $\Delta_{M_3}$ and
  $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.  I'm guessing
  something funny to do with their values and also $m_{Q}^2$ and $M_3$
  at the high scales.  but i need to see the numbers to know.]

>>>>

@@

By contrast the tuning for E$_6$SSM BM2 is very different.  This point
was chosen as it had much lighter gluino mass that is just
above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
not amongst the lowest tuned points, since at that scale the tree
level tuning from $M_{Z^\prime}$ dominates.  However the reduction in
$M_3$ means that $\Delta_{M_3}$ is substantially lower and only
becomes the dominant tuning very close to the GUT scale, giving a
tuning at $10^{16}$ GeV of $\approx 550$, which is far below that of the
other two benchmark points.
